---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eatPrepTBA <a href="https://franikowsp.github.io/eatPrepTBA/"><img src="man/figures/logo.svg" align="right" height="139"/></a>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/franikowsp/eatPrepTBA/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/franikowsp/eatPrepTBA/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of eatPrepTBA is to provide wrapper functions to interact with the IQB Studio and the IQB Testcenter APIs. Moreover, it provides some routines for preparing and blending data from these different resources to manage TBA studies.

## Installation

You can install the development version of eatPrepTBA from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("franikowsp/eatPrepTBA")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(eatPrepTBA)
```
